\newpage
\section{Introduction}
Head-Up Display Auto Alignment System is a project requested by Brandon Wilson of Rockwell Collins. A Head-Up display is a transparent display that is installed in many aircrafts today. Located in the pilot’s forward field of view, a HUD presents flight information by using graphical, numerical and symbolical data. This device eliminates the need for pilots to continually transition from head-down instruments to head-up, out-the window view during critical phases of flight. Currently, a HUD obtains data from an aircraft’s Inertial Measurement Unit (IMU). To display precise and accurate information, the HUD must be carefully aligned to the IRU during installation. However, the current HUD installation process requires specialized equipment and epoxy which is time consuming, costly, and interrupts production line progress for the manufacturer. In addition, the resulting HUD alignment, while precise, does not compensate for airframe droop during flight. \\

Rockwell Collins is looking forward to a new alignment methodology utilizing an inexpensive microelectromechanical systems (MEMS) IRU mounted onto the HUD to infer alignment data from the aircraft precisely mounted and aligned IRU. This project aims to develop a demonstration systems as a proof of concept for Rockwell Collins, that will prove there is a feasible system with an algorithm that is able to output precise and aligned data with reduced installation cost by utilizing data from both the inexpensive MEMS IRU and the aircraft mounted IRU. \\ 

Specifically, our clients team consist of Brandon Wilson, Weston Lahr, and Byron Roethler. Brandon is our main communication line to Rockwell Collins team and supervise our team during the project. Weston give technical reviews for our project and documents. Byron oversees the project. Our team consist of Jiongcheng Luo, Krisna Irawan, and Drew Hamm. Jiongcheng Luo is the leader of the team and in charge of hardware configuration of this project. He is also the main communicator for this team. Krisna Irawan is the manager of the team and in charge of the graphical user interface and statistical analysis portion of this project. Drew Hamm is the main technical person of the team and in charge of the offset algorithm of this project.  \\