\newpage
\section{How did we learn new Technology}
Sparkfun website was helpful to get started with the project, especially the Sparkfun MPU-9250 Hookup Guide article. It has a nice tutorial for the configuration of the hardware. On this website, we can also found the product specification document, and a link to a sample code in Github. This document was crucial for the success of our project. Our team consisted of three computer science students, which gave us a hard time to set up the hardware. This website helped us to set up the hardware and get started with the project. \\

Github was also a great resource for this project. When we are stuck with some problems on this project, we can look for similar open source project and learn the code from there. The only downside of this method was that each open source project has their own method of implementation. This made us had to spend an extra time in examining and understanding each open source projects. Overall, it is a great starting point for our project. \\

Vpython website was crucial for the graphical user interface portion of this project. This website has everything we need to work on the user interface. It has a nice sample code that provide us an example on how to start working with Vpython code. Function documentations that this website has was also helpful to help us understand the syntax of each function. With the computer graphic background that our team have, and the content of this website, we created a nice graphical user interface for this project. \\

Stack Overflow was a great resource for a more specific technical question. It is a community based website, so everybody can ask their question in that website and the community will try their best to answer it. Many of our question for this project was already been asked in this website, which makes this website a great resource for this project. Wikipedia was also a great resource for understanding concepts for this project. It has a nice and straightforward article that explain the concept that we want to learn. \\

MPU-9250 Product Specification Revision 1.0 was a great reference book. This book has everything we need to understand about the MPU-9250. It has a detailed information about features that MPU-9250 has. This book was also critical for the I2C protocol of this project. This book helped us to understand how this MPU works. \\

Special thanks to Matthew Shuman, an OSU faculty member that helped us on this project. Our team consisted of three computer science students, which gave us a hard time to set up the hardware. We consulted with Matthew on how to approach this project. He gave us his thought on the hardware setup, and the design of this project. His thought and expertise was valuable for us to get started on this project. \\
